Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-13 paper.qmd
Updated Figure 7

mse_two_curvy_lwd <- ggplot(error_rm_two_curvy, 
                     aes(x = benchmark_rm_lwd, 
                         y = sqrt(MSE),
                         color = bin1)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.5
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  # scale_x_continuous("standardized bin count", 
  #        transform = "reverse") + 
  scale_x_continuous(breaks = sort(unique(error_rm_two_curvy$benchmark_rm_lwd))[c(1, 3, 5, 7, 9, 11, 13, 15, 17)]) +
  scale_color_manual(values=c("#d95f02", "#1f78b4", "#1b9e77")) +
  xlab("threshold to remove low-density hexagons") +
  ylab("RMSE") +
  interior_annotation("c", position = c(0.1, 0.9), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.title = element_text(size = 18),
axis.text = element_text(size = 15))
```

@@

mse_two_curvy_b + a1_m_two_curvy +
  mse_two_curvy_lwd + prop_dens_a1 +
  plot_layout(ncol=2)
```

>>>>

mse_two_curvy_lwd <- ggplot(error_rm_two_curvy, 
                     aes(x = benchmark_rm_lwd, 
                         y = sqrt(MSE),
                         color = bin1,
                         linetype = bin1)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.5
    ) + 
  scale_x_continuous(breaks = sort(unique(error_rm_two_curvy$benchmark_rm_lwd))[c(1, 3, 5, 7, 9, 11, 13, 15, 17)]) +
  scale_color_manual(values=c("#d95f02", "#1f78b4", "#1b9e77")) +
  scale_linetype_manual(values = c("dashed", "solid", "dotted")) +
  xlab("threshold to remove low-density hexagons") +
  ylab("RMSE") +
  interior_annotation("c", position = c(0.1, 0.9), cex = 2) +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 20, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "bottom",
        axis.title = element_text(size = 18),
axis.text = element_text(size = 15))
```

@@

mse_two_curvy_b + a1_m_two_curvy +
  mse_two_curvy_lwd + prop_dens_a1 +
  plot_layout(ncol=2, guides = "collect")
```
